Sea: A lightweight data-placement library for Big Data scientific computing

### 2022-03-29 paper/sea-comp/paper.tex
updates to comp paper

% \algnewcommand\algorithmicforeach{\textbf{for each}}
% \algdef{S}[FOR]{ForEach}[1]{\algorithmicforeach\ #1\ \algorithmicdo}
% \algblock{Input}{EndInput}
% \algnotext{EndInput}
% \algblock{Output}{EndOutput}
% \algnotext{EndOutput}
% \newcommand{\Desc}[2]{\State \makebox[2em][l]{#1}#2}
\newcommand{\todo}[1]{\marginpar{\parbox{18mm}{\flushleft\tiny\color{red}\textbf{TODO}: #1}}}

% benchmark on beluga, prefreesurfer with RUIS
% use more than 64 subjects for prefreesurfer --> few 100 subjects
% think more about how to benchmark I/O
% try distributed jobs with Sea

\begin{document}
\title{Sea: A lightweight data-management library for Big Data scientific computing}
% remove neuroimaging and replace with scientific computing  add user-space, switch HPC to computing clusters

@@

\IEEEraisesectionheading{\section{Introduction}\label{sec:introduction}}
\IEEEPARstart{E}{fficient} data-placement
strategies have become essential in minimizing the costs of processing Big Data.
Strategies, such as data locality and in-memory computing, improve application runtime by ensuring
data access occur on the most efficient available storage. Existing Big Data frameworks, such as
MapReduce~\cite{dean2008mapreduce}, Apache Spark~\cite{zaharia2016apache} and
Dask~\cite{rocklin2015dask}, improve runtime performance through the incorporation of these data-placement
strategies.

@@

Data-placement strategies can complement existing solutions by selecting where data should be accessed at runtime,
facilitating the transfer and processing of large datasets across different infrastructures, and placing the different
file formats at the preferred storage layer to maximize efficiency. However, converting adapting existing scientific frameworks
and applications to Big Data frameworks requires significant effort, necessitating the rewrite of many well established applications.
Furthermore, as noted in \cite{mehta2017comparative}, Big Data frameworks are still difficult to use for the processing of certain
scientific data, such as imaging data.

%multiple disk support
% pipeline agnostic and pipeline access patterns
% don't leverage workflows
% leverage existing filesystems
% replace storage devices with storage location.
% use applications
% memory management paragraph: PAGE CACHE
% shared filesystems are slow and metadata management can be slow

% add need for userspace / intelligent pipeline flushing
% there is no one-size fits all with data intensive applications
% due to io patterns, so we decided with userspace.

@@

Our goal is to provide a data-placement add-on to standardized scientific computing applications executing on High Performance Computing (HPC)
clusters. The tools of particular interest to us consist of various tasks that communicate to each other via a POSIX-compliant file system. Whereas
they can be platform-agnostic, users typically leverage them within an HPC context, particularly when processing large volumes of data, due to their
inherent reliance on POSIX-compliance.

We developed Sea, a user-space data-placement library, that provides efficient data placement without reinstrumentation of the underlying application.
Given a predefined storage hierarchy, Sea can prefetch, cache, flush and evict data to and from a permanent storage location. To evaluate Sea,
we have designed a performance model, as well as evaluate its performance on a synthetic Big Data application running on a representative neuroimaging dataset.

\section{Related Work}
\subsection{HPC Infrastructure}
      The general structure of HPC clusters may complicate the deployment of Big
      Data frameworks. Typical HPC clusters consist of distinct storage and
      compute nodes. While the compute nodes may also have local storage, there
      is no distributed file system like the Hadoop Distributed File System
      (HDFS)~\cite{shvachko2010hadoop} or Alluxio~\cite{alluxio} to facilitate
      data locality. Furthermore, access to these compute nodes is temporary,
      with allocation duration enforced by a batch scheduler. Therefore, any
      data written to a compute node is inaccessible after the allocation is
      terminated.

      The storage layer found on HPC clusters consists of a high-performance
      parallel file system (PFS) (e.g. Lustre~\cite{lustre}). These file systems
      are shared amongst all compute nodes within a cluster, typically connected
      to each node via high-performance network interconnect such as
      InfiniBand~\cite{infiniband}. I/O overheads of shared PFS can be incurred
      in many places, from the shared network, to the bandwidth of the storage
      disks.  With Lustre specifically, there typically are many data nodes, known as
      Object Storage Servers (OSS) which contain several storage devices, known
      as Object Storage Targets (OST). All file metadata is maintained within a
      separate node known as the Metadata Server (MDS) and stored within a
      device referred to as the Metadata Target (MDT). Although data transfers
      can be communicated directly to the corresponding OST, the clients need to
      first communicate with the MDS to determine which OST to communicate with.
      This can result in major data transfer overheads, particularly when making
      numerous requests to the metadata server.

      HPC clusters may provide a faster additional storage layer, known as a
      Burst Buffer, aimed at improving I/O performance. A Burst Buffer typically
      consists of fast storage (SSD and memory) and can be local to the compute
      node or as a dedicated I/O node. It was introduced as a response to offset
      the impacts of large-scale application checkpointing on the PFS~\cite{bb}. The
      application would write a checkpoint to the Burst Buffer and resume
      processing, while the checkpoint would be asynchronously flushed to the
      PFS.

@@

      Strategies mitigate the impacts of data transfers in data-intensive workloads is
      required. In text-based processing, frameworks such as
      MapReduce~\cite{dean2008mapreduce} and Apache
      Spark~\cite{zaharia2016apache} have implemented and popularized strategies
      to minimize the need for data transfers during processing. These
      strategies are known as data locality and in-memory computing.

      Data locality is the process by which compute tasks are scheduled nearest
      to where the data is located. Traditionally, storage and compute were kept
      separate, having to transfer data over the network to compute. Rather than
      having to transfer large amounts of data over the network to the compute
      tasks, which could incur significant overheads, Big Data frameworks ensure
      that data is stored directly on the compute nodes. When a compute task
      requires access to specific data, the scheduler sends the task to the
      nearest available node to the data, thereby minimizing any cost of
      network-related data transfers. This strategy is not only used by Big Data
      Frameworks such as Hadoop MapReduce, Apache Spark, and
      Dask~\cite{rocklin2015dask}, but also enabled by file systems such as HDFS
      and Alluxio.

\subsection{The Linux page cache}
 While scientific applications uncommonly use Big Data frameworks and must
      perform large over-the-network data transfers, they may still benefit from
      in-memory computing and data locality through the Linux Page
      Cache~\cite{pagecache}. Similarly to other file systems, Lustre leverages
      the client node page cache to reduce I/O overheads. System memory is
      composed of two components: 1) anonymous memory and 2) page cache.
      Anonymous memory consists of all application-related objects, whereas page
      cache consists of recently accessed file data. When a file is read, that
      file is loaded up into the page cache to be flagged for eviction based on
      a least recently used (LRU) policy. That means subsequent accesses to that
      data may be done entirely in memory so long as that data has not already
      been evicted. Similarly, for writes to a file system with writeback cache
      enabled, the file will be written to memory completing the write operation
      once the file has been written entirely to memory. That file will then be
      flushed asynchronously to the appropriate storage device. As system memory
      may get overloaded with too many write requests, there is a limit to the
      amount of written data that can exist in memory, known as the
      \texttt{dirty\_ratio}. Furthermore, applications producing too many write
      requests may be throttled by the system.

\subsection{File System implementations}
      Due to the architecture of conventional HPC clusters, network-based
      parallel files systems are favoured over Big Data distributed file
      systems. Such file systems require super-user access, preventing users
      from deploying their own on-the-fly cluster. While HDFS can be loaded
      in user-space by mounting its File System in Userspace (FUSE)
      implementation, FUSE-based file systems can perform significantly worse
      than desired, depending on the application~\cite{tofuse}. Even with a
      user-space version of HDFS, there would be no mechanism to transfer all
      the data back to the parallel file system to be accessible post resource
      requests. Furthermore, such file systems are not POSIX-compliant, which
      would be required for scientific computing applications.

      There are, however, Big Data file systems, such as
      XtreemFS~\cite{xtreemfs} that exist entirely within user space, are
      POSIX-compliant, and can use alternative methods to FUSE to function.
      XtreemFS uses the LD\_PRELOAD trick to intercept file system calls made to
      the GNU C library (glibc). There are limitations to using glibc
      interception. For instance, the application must be dynamically linked and
      make glibc calls. However, statically-linked applications are uncommon and
      applications interacting with POSIX-compliant file systems on Linux
      machines, the predominant OS of HPC clusters, will make glibc calls.
      Nevertheless, there are alternatives to glibc intercept that can bypass
      the aforementioned issues, such as system call interception, but they
      result in greater overheads~\cite{quinson}.

      Characteristics that make XtreemFS unlikely to be deployed on-the-fly
      include complex file system deployment and configuration properties. It
      also does not provide a simple way to leverage different classes of
      storage devices, nor ensure that required data will be copied to the
      cluster's parallel file system.

      BurstFS~\cite{burstfs} and GekkoFS~\cite{gekkofs} are two user-space file
      systems that are specifically designed for Burst Buffers. That is, both of
      these file systems exist only during the time-window in which the
      resources are allocated. Furthermore, they both exist entirely within
      user-space using glibc interception. While these implementations simplify
      usage of burst buffers for users, their installation and configuration would be out of the
      scope of a typical HPC user and thus require sysadmin intervention.
\section{Materials and Methods}

@@

    \centering
    \includegraphics[width=\columnwidth]{figures/seacomp-diagram.pdf}%
\caption{The Sea data-management library. Sea intercepts I/O-related glibc calls issued by the application and
translates the path provided if located within the Sea mountpoint. Sea leverages a user-defined storage hierarchy to help select the most appropriate path and the redirects the call to glibc to process the request on the translated path. }
\label{fig:sea-comp:diagram}
\end{figure*}

Sea\footnote{\url{https://github.com/valhayot/sea}} is an open-source user-space
data-placement C++ library for applications running on HPC systems. Its main
aim is to reduce application data transfer costs by leveraging node-local
storage (Figure~\ref{fig:sea-comp:diagram}). Sea redirects files accessed from a user-specified mount point to the
appropriate storage devices using glibc interception. Within an intercepted call
the file will be written to or read from the fastest storage device available.

At minimum, Sea requires the user to specify at least two storage devices, a
fast temporary one (i.e. cache) and a slower long-term storage one. This could be RAM and SSD
if working on a single node, or a compute-local SSD and a shared parallel file
system, in the case of an HPC cluster. Ideally, a user will provide a multitude
of short-term storage devices to improve Sea's efficacy. Furthermore, to
maximize usage of the fastest available storage devices, Sea will allow the user
to outline which files can be removed from short-term storage in addition to
which files need to be materialized onto long-term storage. Eviction of files is
important as this will allow Sea to maximize usage of short-term storage.

Sea was meant as a data-management service to be employed at the discretion of
the users on scientific applications. When coming up with the idea for Sea, we
observed the design differences between Big Data and scientific, specifically
neuroimaging, frameworks and applications. Scientific frameworks tend to favour
ease-of-use, reproducibility, portability and parallelism over minimizing data
transfers. It was important for us to ensure that Sea would preserve the design
decisions of the underlying tools. Sea achieves this by having few dependencies,
is lightweight, and requires minimal configuration.

@@

Sea is primarily designed to work with workloads that generate large amounts of
intermediate data. Since data must be read from the slower storage device and
final output data most likely would have to be written to the same device, the
use of Sea with workloads that do not produce intermediate data would result in
limited speedup and may even introduce some overheads.

Sea provides two main modes based on flushing specification: In-memory computing
and flush-all. In-memory computing is achieved when intermediate need not be
materialized to long-term storage (i.e. no flushing). With Sea in-memory, we can
expect speedups comparable to Big Data frameworks.

As the name implies, Sea flush-all is achieved when all data must be
materialized to long-term storage (i.e. flush everything). This can be coupled
with eviction to limit the amount of data that will be written to slower, but
larger local storage devices. While this option will have overheads, due to the
need to flush all application data, performance can be improved when data
transfers and compute time are similar.

@@

Our tests have been executed on three different operating systems: Ubuntu (xenial, bionic, focal),
Fedora (32, 33, 34) and Centos (6, 7). Using this test matrix, the Sea tests were able to span seven glibc
versions ranging from 2.17 to 2.33. As glibc file system functions may change over time, Sea behaviour with
newer and older versions of glibc is undefined. 
% ldd (GNU libc) 2.17
% ldd (Ubuntu GLIBC 2.23-0ubuntu11.3) 2.23
% ldd (Ubuntu GLIBC 2.27-3ubuntu1.4) 2.27
% ldd (GNU libc) 2.28
% ldd (Ubuntu GLIBC 2.31-0ubuntu9.2) 2.31
% ldd (GNU libc) 2.31
% ldd (GNU libc) 2.32
% ldd (GNU libc) 2.33

@@

      We use the BigBrain~\cite{amunts2013bigbrain}, a one-of-a-kind histology
      dataset of the human brain, as a representative scientific dataset. For
      all our experiments, we utilize the \SI{20}{\micro\meter} dataset, which
      totals to approximately \SI{603}{\gibi\byte}. The dataset was broken down
      into 1000 files each consisting of \SI{617}{\mebi\byte} of data.
      %of data as well as
      %5000 blocks each \SI{124}{\mebi\byte} in size.

@@

% if have a single appendix:
%\appendix[Proof of the Zonklar Equations]
% or
%\appendix  % for no appendix heading
% do not use \section anymore after \appendix, only \section*
% is possibly needed

% use appendices with more than one appendix
% then use \section to start each appendix
% you must declare a \section before using any
% \subsection or using \label (\appendices by itself
% starts a section numbered zero.)
%

\appendices
% you can choose not to have a title for an appendix
% if you want by leaving the argument blank
\section{}
Appendix two text goes here.

@@

% % Can use something like this to put references on a page
% % by themselves when using endfloat and the captionsoff option.
% \ifCLASSOPTIONcaptionsoff
%   \newpage
% \fi
\bibliographystyle{plain}
\bibliography{biblio}

>>>>

% \algnewcommand\algorithmicforeach{\textbf{for each}}
% \algdef{S}[FOR]{ForEach}[1]{\algorithmicforeach\ #1\ \algorithmicdo}
% \algblock{Input}{EndInput} \algnotext{EndInput} \algblock{Output}{EndOutput}
% \algnotext{EndOutput} \newcommand{\Desc}[2]{\State \makebox[2em][l]{#1}#2}
\newcommand{\todo}[1]{\marginpar{\parbox{18mm}{\flushleft\tiny\color{red}\textbf{TODO}:
#1}}}

% benchmark on beluga, prefreesurfer with RUIS use more than 64 subjects for
% prefreesurfer --> few 100 subjects think more about how to benchmark I/O try
% distributed jobs with Sea

\begin{document}
\title{Sea: A lightweight data-placement library for Big Data scientific computing}
% remove neuroimaging and replace with scientific computing  add user-space,
% switch HPC to computing clusters

@@

\IEEEraisesectionheading{\section{Introduction}\label{sec:introduction}}
\IEEEPARstart{E}{fficient} data-placement strategies have become essential in
minimizing Big Data processing overheads. These strategies, such as data
locality and in-memory computing, improve application runtime by ensuring data
accesses occur on the most efficient available storage. Existing Big Data
frameworks, such as MapReduce~\cite{dean2008mapreduce}, Apache
Spark~\cite{zaharia2016apache} and Dask~\cite{rocklin2015dask}, improve runtime
performance through the incorporation of these data-placement strategies.

@@

Data-placement strategies can complement existing solutions by facilitating the
transfer and processing of large datasets across different infrastructures, and
placing the different file formats at the preferred storage layer to maximize
efficiency. However, adapting existing scientific applications to Big Data
frameworks requires considerable effort, necessitating the rewrite of many well
established applications. Furthermore, as noted in \cite{mehta2017comparative},
Big Data frameworks are not easy to use for the processing of certain scientific
data, such as imaging data, due to the level of expertise required to rewrite
reference implementations using the frameworks.

%multiple disk support pipeline agnostic and pipeline access patterns don't
% leverage workflows leverage existing filesystems replace storage devices with
% storage location. use applications memory management paragraph: PAGE CACHE
% shared filesystems are slow and metadata management can be slow

% add need for userspace / intelligent pipeline flushing there is no one-size
% fits all with data intensive applications due to io patterns, so we decided
% with userspace.

@@

Our goal is to provide a data-placement solution to standardized scientific
computing applications executing on High Performance Computing (HPC) clusters.
The tools of particular interest to us consist of various tasks that communicate
to each other via a POSIX-compliant file system. Whereas the tools can be
platform-agnostic, we assume users will leverage them within an HPC context,
particularly when processing large volumes of data, due to their inherent
reliance on POSIX-compliance.

We developed Sea, a user-space data-placement library, that provides efficient
data placement without reinstrumentation of the underlying application. Given a
predefined storage hierarchy, Sea can prefetch, cache, flush and evict data to
and from a permanent storage location. To assist in providing a
frame-of-reference for Sea's performance on HPC systems, we designed a
performance model. We then evaluated Sea's performance on a synthetic Big Data
application running on a representative neuroimaging dataset, comparing its
performance with the bounds delineated by the model.

\section{Related Work}
\subsection{HPC Infrastructure}
      The general structure of HPC clusters complicates the deployment of Big
      Data frameworks. Typical HPC clusters consist of distinct storage and
      compute nodes. While compute nodes may also have local storage, there is
      no distributed file system like the Hadoop Distributed File System
      (HDFS)~\cite{shvachko2010hadoop} or Alluxio~\cite{alluxio} to facilitate
      data locality. Furthermore, access to these compute nodes is temporary,
      with allocation duration enforced by a batch scheduler. Therefore, any
      data written to compute nodes are rendered inaccessible after the
      allocation is terminated.

      The storage layer found on HPC clusters consists of a high-performance
      parallel file system (PFS) (e.g. Lustre~\cite{lustre}). These file systems
      are shared amongst all compute nodes within a cluster, typically connected
      to each node via high-performance network interconnect such as
      InfiniBand~\cite{infiniband}. I/O overheads of shared PFS can be incurred
      in many places, from the shared network to the bandwidth and latency of
      the storage devices.  With Lustre specifically, there typically are many
      data nodes, known as Object Storage Servers (OSS) which contain several
      storage devices, known as Object Storage Targets (OST). All file metadata
      is maintained within a separate node known as the Metadata Server (MDS)
      and stored within a device referred to as the Metadata Target (MDT).
      Although data transfers can be communicated directly to the corresponding
      OST, the clients need to first communicate with the MDS to determine which
      OST to communicate with. This can result in major data transfer overheads,
      particularly when making numerous requests to the metadata server.

      HPC clusters may provide a faster intermediate storage layer, known as a
      Burst Buffer, aimed at improving I/O performance. A Burst Buffer typically
      consists of higher-performance storage devices (SSD and memory) and can be
      local to the compute node or as a dedicated I/O node. Burst Buffers were
      introduced as a response to offset the impacts of large-scale application
      checkpointing on the PFS~\cite{bb}. The application would write a
      checkpoint to the Burst Buffer and resume processing, while the checkpoint
      would be asynchronously flushed to the PFS.

@@

      Strategies to mitigate the impacts of data transfers in data-intensive
      workloads are required to ensure optimal processing time. Early Big Data
      frameworks, notably MapReduce~\cite{dean2008mapreduce} and Apache
      Spark~\cite{zaharia2016apache} have implemented and popularized
      data-management strategies to minimize data transfers at processing time.
      These strategies are known as data locality and in-memory computing.

      Data locality ensures that compute tasks are scheduled nearest to where
      the data is located. Historically, storage and compute nodes were distinct
      layers, data transfer to the compute location. Rather than transferring
      large amounts of data over the network to compute tasks, which could incur
      significant overheads, Big Data frameworks ensure that data is stored
      directly on the compute nodes. When a compute task requires access to
      specific data, the scheduler sends the task to the nearest available node
      to the data, thereby minimizing any cost of network-related data
      transfers. This strategy is not only used by Big Data Frameworks such as
      Hadoop MapReduce, Apache Spark, and Dask~\cite{rocklin2015dask}, but also
      enabled by file systems such as HDFS and Alluxio.

      In-memory computing complements data locality by maximizing use of
      available memory to maintain intermediate data. Whereas with data locality
      alone, tasks would leverage local storage, typically in the form of HDDs
      or SSD, to maintain task input and output data, with the addition of
      in-memory computing, data would be stored in main memory to minimize
      latency and maximize bandwidth.

      While Big Data frameworks and filesystems are not commonly used in HPC,
      HPC clusters are typically Linux-based and benefit from the Linux page
      cache, which can provide data locality and in-memory computing at a
      limited capacity. Furthermore, HPC architectures may also provide an
      intermediate storage layer, known as a Burst Buffer, to improve
      application I/O-related overheads. To facilitate an applications
      interaction between application and storage layer, distributed file
      systems have been developed.

\subsection{The Linux page cache}
 While scientific applications do not customarily leverage data-placement
      strategies and may perform large over-the-network data transfers, they may
      still benefit from in-memory computing and data locality through the Linux
      Page Cache~\cite{pagecache}. Similarly to other file systems, Lustre
      leverages the compute node page cache to reduce I/O overheads. System
      memory is composed of two components: 1) anonymous memory and 2) page
      cache. Anonymous memory consists of all application-related objects,
      whereas page cache consists of recently accessed file data. When a file is
      read, that file is loaded up into the page cache to be flagged for
      eviction based on a least recently used (LRU) policy. That means
      subsequent accesses to that data may be done entirely in memory so long as
      that data has not already been evicted. Similarly, for writes to a file
      system with writeback cache enabled, the file will be written to memory
      completing the write operation once the file has been written entirely to
      memory. That file will then be flushed asynchronously to the appropriate
      storage device. As system memory may get overloaded with too many write
      requests, there is a limit to the amount of written data that can exist in
      memory, known as the dirty\_ratio. Furthermore, applications producing too
      many write requests may be throttled by the system.

\subsection{File System implementations}
      Due to the architecture of conventional HPC clusters, network-based
      parallel files systems are favoured over Big Data distributed file
      systems. Such file systems require super-user access, preventing users
      from deploying their own on-the-fly cluster. While HDFS can be loaded in
      user-space by mounting its FUSE (Filesystem in User Space) implementation,
      FUSE-based file systems may perform significantly worse than desired,
      depending on the application~\cite{tofuse}. Even with a user-space version
      of HDFS, there would be no mechanism to transfer all the data back to the
      PFS post-processing.
      % Furthermore, such file systems are not POSIX-compliant, which would be
      % required for scientific computing applications.

      However, there exist Big Data file systems, such as
      XtreemFS~\cite{xtreemfs}, that exist entirely within user space, are
      POSIX-compliant, and can use alternative methods to FUSE to function. For
      instance, XtreemFS uses the LD\_PRELOAD trick to intercept file system
      calls made to the GNU C library (glibc). There are limitations to using
      glibc interception; the application must be dynamically linked and make
      glibc calls. However, statically-linked applications are uncommon and
      applications interacting with POSIX-compliant file systems on Linux
      machines, the predominant OS of HPC clusters, will make glibc calls.
      Nevertheless, there are alternatives to glibc intercept that can bypass
      the aforementioned issues, such as system call interception, but they
      result in greater overheads~\cite{quinson}.

      Due to complex file system deployment and configuration properties,
      XtreemFS is unlikely to be deployed on an ephemeral burst buffer. It also
      does not provide a simple way to leverage different classes of storage
      devices, nor ensure that required data will be copied to the cluster's
      parallel file system.

      BurstFS~\cite{burstfs} and GekkoFS~\cite{gekkofs} are two user-space file
      systems that are specifically designed for Burst Buffers. That is, both of
      these file systems exist only during the time-window in which the
      resources are allocated. Furthermore, they both exist entirely within
      user-space using glibc interception. While these implementations simplify
      usage of burst buffers for users, their installation and configuration is
      similarly out-of-scope for a typical HPC user.

\section{Materials and Methods}

@@

    \centering
    \includegraphics[width=\columnwidth]{figures/seacomp-diagram.pdf}%
\caption{The Sea data-placement library. Sea intercepts I/O-related glibc calls
issued by the application and translates the path provided if located within the
Sea mountpoint. Sea leverages a user-defined storage hierarchy to help select
the most appropriate path and the redirects the call to glibc to process the
request on the translated path. }
\label{fig:sea-comp:diagram}
\end{figure*}

Sea\footnote{\url{https://github.com/big-data-lab-team/sea}} is an open-source
user-space data-placement C++ library for applications running on HPC systems.
Its main aim is to reduce application data transfer costs by leveraging
node-local storage (Figure~\ref{fig:sea-comp:diagram}). Sea redirects files
accessed from a user-specified mount point to the appropriate storage devices
using glibc interception. Within an intercepted call the file will be written to
or read from the fastest storage device available.

Sea requires minimal configuration for use. In order to work, Sea requires the
user to specify at least two storage devices, a fast temporary one (i.e. cache)
and a slower long-term storage one. This could be RAM and SSD if working on a
single node, or a compute-local SSD and a shared parallel file system, in the
case of an HPC cluster. Ideally, a user will provide a multitude of ephemeral
storage devices to improve Sea's efficacy. Furthermore, to maximize usage of the
fastest available storage devices, Sea will allow the user to outline which
files can be removed from short-term storage in addition to which files need to
be materialized onto long-term storage. Eviction of files is important as this
will allow Sea to maximize usage of short-term storage.

Sea was created as a data-placement service to be employed at the discretion of
the users on scientific applications. When developing the idea for Sea, we
observed the design differences between Big Data and scientific, specifically
neuroimaging, frameworks and applications. Scientific frameworks and
applications tend to favour ease-of-use, reproducibility, portability and
parallelism over minimizing data
transfers\cite{jarecka2020pydra,esteban2019fmriprep,wagner2022fairly}. It was
important for us to ensure that Sea would preserve the design decisions of the
underlying tools. Sea achieves this by having few dependencies, is lightweight,
and requires minimal configuration.

@@

Sea is primarily designed to work with workloads that generate large amounts of
intermediate data. Since data must be read from the slower storage device and final outputs will
also have to be written to the same device, the
use of Sea with workloads that do not produce intermediate data would result in
limited speedup and may even introduce some overheads.

Sea provides two main modes based on flushing specification: In-memory computing
and copy-all. In-memory computing is achieved when intermediate need not be
materialized to long-term storage (i.e. no flushing). With Sea in-memory, we can
expect speedups comparable to Big Data frameworks.

As the name implies, Sea copy-all is applicable when all data must be
materialized to long-term storage (i.e. flush everything). This can be coupled
with eviction to limit the amount of data that will be written to slower, but
larger, local storage devices. While this option will have overheads, due to the
need to flush all application data, overheads will be negligible when data transfer and compute time
are similar.

@@

Our tests have been executed on three different operating systems: Ubuntu
(xenial, bionic, focal), Fedora (32, 33, 34) and Centos (6, 7). Using this test
matrix, the Sea tests were able to span seven glibc versions ranging from 2.17
to 2.33. As glibc file system functions may change over time, Sea behaviour with
newer and older versions of glibc is undefined. 
% ldd (GNU libc) 2.17 ldd (Ubuntu GLIBC 2.23-0ubuntu11.3) 2.23 ldd (Ubuntu GLIBC
% 2.27-3ubuntu1.4) 2.27 ldd (GNU libc) 2.28 ldd (Ubuntu GLIBC 2.31-0ubuntu9.2)
% 2.31 ldd (GNU libc) 2.31 ldd (GNU libc) 2.32 ldd (GNU libc) 2.33

@@

      We use the BigBrain~\cite{amunts2013bigbrain}, a one-of-a-kind histology
      dataset of the human brain, as a representative scientific dataset. For
      all our experiments, we utilize the \SI{20}{\micro\meter} dataset, which
      totals to approximately \SI{603}{\gibi\byte}. The dataset was broken down
      into 1000 files each consisting of \SI{617}{\mebi\byte} of data.
      %of data as well as 5000 blocks each \SI{124}{\mebi\byte} in size.

@@

% if have a single appendix: \appendix[Proof of the Zonklar Equations] or
%\appendix  % for no appendix heading do not use \section anymore after
%\appendix, only \section* is possibly needed

% use appendices with more than one appendix then use \section to start each
% appendix you must declare a \section before using any \subsection or using
% \label (\appendices by itself starts a section numbered zero.)
%

\appendices
% you can choose not to have a title for an appendix if you want by leaving the
% argument blank
\section{}
Appendix two text goes here.

@@

% % Can use something like this to put references on a page % by themselves when
% using endfloat and the captionsoff option. \ifCLASSOPTIONcaptionsoff \newpage
% \fi
\bibliographystyle{plain}
\bibliography{biblio}
